Report

### 2022-08-01 manuscript.Rmd
elaborate further on effect of design factors

```{r, fig.cap="Mean performance by reliability"}
df_plot <- melt(res, measure.vars = c("sensitivity", "specificity"),
             variable.name = "Outcome", value.name = "val")
# df_plot <- df_plot[ ,list(mean=mean(val)), by=c("reliability", "Outcome", "alg")]
df_plot <- as.data.frame(df_plot)
df_plot <- aggregate(df_plot$val, df_plot[c("reliability", "Outcome", "alg")], FUN=mean)
names(df_plot)[ncol(df_plot)] <- "mean"
ggplot(df_plot, aes(x = reliability, y = mean, group = interaction(Outcome, alg), shape = alg, linetype = Outcome)) +
  geom_point() +
  geom_line() +
  theme_bw() +
  labs(y = "Mean performance", x = "Reliability")
```

@@

This simulation study validated the product Bayes factor as an alternative method to synthesize evidence across studies.
The PBF was benchmarked against other common methods for evidence synthesis.
This was done by calculating the accuracy, sensitivity and specificity of the methods in different plausible varying conditions.

Within the scope of this simulation, PBF had relatively better inferential properties <!-- EB: higher accuracy --> than the other algorithms under consideration.
Although other algorithms had superior specificity, PBF had the highest levels of sensitivity.
Thus, PBF balanced the ability to accept an informative hypothesis in the presence of a true population effect with the ability to reject the hypothesis when there was no effect.

An important caveat is that none of the algorithms met conventional criteria for power (80%) and type I error (5%).
Overall, PBF had the best performance, with a power of 76% and type I error of 24%.
Thus, if researchers intend to synthesize evidence for an informative hypothesis across heterogeneous studies, PBF may be the most suitable method - but its limitations <!-- higher probability for type 1 errors --> should be acknowledged in applied research.

@@

The overall performance of PBF increased most with increasing sample size.
PBF's sensitivity was .57 when a sample size of 20 per sample was simulated, while for all other algorithms this was below .11.
Even at a sample size of 500, the sensitivity of the other algorithms only rose slightly above .60, 
while for PBF this was .90.
This provides evidence that state-of-the-art evidence synthesis methods have little power to detect a true effect.
PBF on the other hand presents itself as a small sample size solution for evidence synthesis methods to detect true effects.
This is reflected in the accuracy of the algorithms at small sample sizes.
The accuracy at a sample size of 20, was around .50 for RMA, IPD and VC.
This can be attributed to their low sensitivity and their specificity that is at ceiling level. 
By consistently not finding an effect, the algorithms are correct 50\% of the time.
At all sample sizes, the PBF was the most accurate algorithm,
although it should be noted that even at a sample size of 500, PBFs specificity was .12 percentage points too low for conventional acceptable type I error rates.

With an increasing number of groups, slightly decreasing specificity was traded off for increasing sensitivity.<!-- I would argue that the decrease is negligable, 0.767 at k =2, 0.763 at k = 10 -->
With an increasing number of groups, specificity remained around .76 for PBF, while sensitivity increased to .87.
Again, the specificity remained at ceiling level for the other algorithms.
The sensitivity for RMA and IPD increased, but stayed below .51.
In a similar way, this supports the use of the PBF as a small sample size solution.
In this case when there are little available studies to synthesize evidence over.
Even with as much as ten available studies, PBF was the only algorithm that has a conventionally acceptable power.

With increasing reliability, increasing specificity was traded off for decreasing sensitivity.

There was no marginal condition in which the PBF had a conventional acceptable type I error rate.
Its mean was .76 which is almost .20 percentage points below .95.
However, the other algorithms had no marginal condition where an acceptable power was achieved.
The PBF can be used as a small sample size solution,
although its increased type I error rate must be taken into account.
It implies that PBF works best as a complementary method for evidence synthesis, rather than a replacement.

>>>>

<!--EB: I think reliability plot is a bit confusing (The one that is saved under ./manuscript_files/figure-latex/unnamed-chunk-3-1.png). That is because the x-axis is labeled 'reliability', but the values are the values of the 'errorsd' condition. This makes that the reliability decreases, rather than increases as you move away from the origin on the x-axis -->
```{r, fig.cap="Mean performance by reliability"}
df_plot <- melt(res, measure.vars = c("sensitivity", "specificity"),
             variable.name = "Outcome", value.name = "val")
# df_plot <- df_plot[ ,list(mean=mean(val)), by=c("reliability", "Outcome", "alg")]
df_plot <- as.data.frame(df_plot)
df_plot <- aggregate(df_plot$val, df_plot[c("reliability", "Outcome", "alg")], FUN=mean)
names(df_plot)[ncol(df_plot)] <- "mean"
ggplot(df_plot, aes(x = reliability, y = mean, group = interaction(Outcome, alg), shape = alg, linetype = Outcome)) +
  geom_point() +
  geom_line() +
  theme_bw() +
  labs(y = "Mean performance", x = "Reliability")
```

@@

This simulation study validated the product Bayes factor as an alternative method to synthesize evidence across studies.
The PBF was benchmarked against other common methods for evidence synthesis.
This was done by calculating the accuracy, sensitivity and specificity of the methods in different plausible varying conditions.
During the simulation the hypotheses remained constant $H_i: \rho > .1$, $H_0: \rho = .1$.
To be able to calculate both sensitivity and specificity, half of the simulated conditions contained an effect, $\rho = .2$, while the other half did not, $\rho = .1$.
<!-- EB: I don't know why we did not use H0:r=0 and Hi:r>0 as constant hypotheses. It seems more intuitive -->
Sensitivity and specificity can be interpreted as Type I error rate and statistical power respectively and are used interchangeably.
 <!-- Because Type 1 error rate and power seem to be key terms in the discussion, we may be able to include it in the introduction: 'How does the PBF compare to other state-of-the-art algorithms with regards to Type 1 error rate, power and overall accuracy?' -->

The overall performance of PBF increased most with increasing sample size.
 <!-- EB: also, shall we rename 'performance' to 'accuracy', I know its not the same, but performance seems a bit too subjective. After all, we do not have a clear cut decision when sensitivity and specificity is balanced 'correctly' --> 
PBF's sensitivity was .57 when a sample size of 20 per sample was simulated, while for all other algorithms this was below .11.
It should be noted that in the condition where sensitivity could be calculated, the true effect $\rho$ was .2 and only .1 points above the boundary value for $H_i > .1$ and $H_0 = .1$.
It is no surprise that at smaller samples, the small difference in effect size between null/informative hypothesis and true value of .1, is unlikely to be detected.
Still, even at a relatively large sample size of 500 per sample, the sensitivity of the other algorithms only rose slightly above .60, 
while for PBF this was .90.
This provides evidence that state-of-the-art evidence synthesis methods have little power to detect a true, but small effect,
even when the sample size per sample was substantial.
PBF on the other hand presents itself as a small sample size solution for evidence synthesis methods to detect true effects,
even if the effect itself can be considered small.
This is also reflected in the accuracy of the algorithms at small sample sizes, which, at a sample size of 20, was around .50 for RMA, IPD and VC.
This can be attributed to their low sensitivity and their specificity that is at ceiling level. 
By consistently not finding an effect, the algorithms are correct 50\% of the time.
At all sample sizes, the PBF was the most accurate algorithm,
although it should be noted that even at a sample size of 500, PBFs specificity was .12 percentage points too high for conventional acceptable type I error rates of .05.

With an increasing number of groups, slightly decreasing specificity was traded off for increasing sensitivity.<!--EB: I would argue that the decrease is negligible, 0.767 at k =2, 0.763 at k = 10 -->
With an increasing number of groups, specificity remained around .76 for PBF, while sensitivity increased to .87.
Again, the specificity remained at ceiling level for the other algorithms.
The sensitivity for RMA and IPD increased, but stayed below .51.
In a similar way, this supports the use of the PBF as a small sample size solution.
In this case when there are little available studies to synthesize evidence over.
It could be argued that when there are only 2 or 3 studies available to synthesize evidence over, that if a trade-off need be made, specificity is preferred over sensitivity.
It seems unwise to more easily acknowledge an effect if there is little data available.
However, the quality of the included studies should be considered before synthesizing evidence in any way.
Moreover, when the researcher performs some form of evidence synthesis, then the ability of the method to find an effect is a necessary and fair component, even if little studies are available.
Also, even with as much as ten available studies, PBF was the only algorithm that had a conventionally acceptable power.

With increasing reliability, increasing specificity was traded off for decreasing sensitivity for PBF. <!--EB: I think its the other way around; with DECREASING reliability, specificity increases and sensitivity decreases, see my comment at the section: 'Effect of reliability' -->
With increasing reliability, decreasing specificity was traded off for increasing sensitivity for the PBF.
Also for the other algorithms, the sensitivity increased as the reliability increased.
It implies that the PBF gets more conservative whenever reliability decreases.
This can be considered beneficial as the PBF is more hesitant to acknowledge an effect as the measurements become less stable.
Even at the smallest acceptable reliability, $\alpha = .6$, PBFs sensitivity was .57, where it was below .10 for the other algorithms.
However, the specificity of the PBF when there is perfect reliability $\alpha=1$ was .63, were it was almost 1 for the other algorithms.

Overall, there was only a single marginal condition where the accuracy of PBF was lower than that of any other algorithm.
PBF scored .01-.02 percentage points lower accuracy than IPD and RMA when there was perfect reliability.
Looking at the specificity and sensitivity however, this is explained by the relatively low specificity of PBF and the very high specificity of RMA and IPD.
Thus,
Within the scope of this simulation, PBF had relatively better inferential properties <!-- EB: higher accuracy --> than the other algorithms under consideration.
Although other algorithms had superior specificity, PBF had the highest levels of sensitivity.
Thus, PBF balanced the ability to accept an informative hypothesis in the presence of a true population effect with the ability to reject the hypothesis when there was no effect.

An important caveat is that none of the algorithms met conventional criteria for power (80%) and type I error (5%) [@cohen2013statistical].
Overall, PBF had the best performance, with a power of 76% and type I error of 24%.
Thus, if researchers intend to synthesize evidence for an informative hypothesis across heterogeneous studies, PBF may be the most suitable method - but its limitations <!-- higher probability for type 1 errors --> should be acknowledged in applied research.

As stated earlier, the PBF can be used as a small sample size solution,
although its increased type I error rate must be taken into account.
It implies that PBF works best as a complementary method for evidence synthesis, rather than a replacement.

@@
